---
title: "Women Live Longer?"
author: "Hardik Monga"
---

# Libraries Used

```{r}
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
```

# age Dataset - Import, Skim, Inspect

```{r}
age <- read_delim(file = "../../data/age-dataset.csv", delim = ";")
age
```

```{r}
skim(women)
inspect(women)
```

# Filtering the dataset for the year 2015

```{r}
year2015_age <- age %>%
    filter(Year == 2015)

year2015_age



```

# Renaming the column names and Putting Decimal points on the Life Expectancy column values

```{r}


new_year2015_age <- year2015_age %>%
  rename(
    ent = Entity,
    code = Code,
    year = Year,
    female_expc = `Life expectancy - Sex: female - Age: at birth - Variant: estimates`,
    male_expc = `Life expectancy - Sex: male - Age: at birth - Variant: estimates`,
    pop = `Population - Sex: all - Age: all - Variant: estimates`,
    cont = Continent
    )

new_year2015_age <- new_year2015_age %>%
  mutate(female_expc = sprintf("%.1f", female_expc / 10),
         male_expc = sprintf("%.1f", male_expc / 10),
         )

new_year2015_age
```

# Variable Types

**Quantitative Variables:** female_expc, male_expc, pop

**Qualitative Variables:** ent, code, year, cont

**Target Variable**: female_expc, male_expc

**Predictor variables**: pop

# Plotting the ScatterPlot Graph

```{r}
new_year2015_age <- new_year2015_age %>%
  mutate(
    male_expc = as.numeric(as.character(male_expc)),
    female_expc = as.numeric(as.character(female_expc))
  )

new_year2015_age %>%
  gf_point(male_expc ~ female_expc, size = ~pop, shape = 1) %>% 
  gf_refine(annotate("text", x = 70, y = 75, label = "Slope = 1")) %>% 
  gf_lm(title = "Life Expectancy Across Countries and Years")

```

# Inference:

I was not able to plot this graph as desired. Will try to figure out the reasons in the future. The first thing that I am able to deduce from this graph is that countries with larger populations have a life expectancy from 65-75 years. It also seems that, women live 5-10 years longer than men.
