---
title: "Veg Non Veg"
author: "Hardik Monga"
---

```{r}
library(tidyverse)
library(mosaic)
library(skimr)
library(dplyr)
library(ggformula)
library(crosstable)
library(ggridges)
```

```{r}
tip_data<- read_delim(file = "../../data/tip.csv")
tip_data
inspect(tip_data)
skim(tip_data)
glimpse(tip_data)
```

```{r}

tip_mod <- tip_data %>%
  dplyr::mutate(
    pref = as_factor(`Food preferance`))
tip_mod
```

```{r}
tip_mod%>%
  group_by(Gender) %>% 
  summarize(average_tip = mean(Tip),count = n())

tip_mod%>%
  group_by(pref) %>% 
  summarize(average_tip = mean(Tip),count = n())
```

```{r}
tip_mod%>%crosstable(Tip~pref) %>% as_flextable()
```

```{r}
mosaic::t_test(Tip~pref, data = tip_mod) %>%  broom::tidy()
```

```{r}
gf_histogram(~Tip, fill = ~pref, data = tip_mod) %>% 
  gf_labs(
    title = "Tips: Veg vs Non-Veg"
  )

gf_histogram(~Tip, fill = ~Gender, data = tip_mod) %>% 
  gf_labs(
    title = "Tips: Male vs Female"
  )
```

```{r}
gf_density_ridges(pref ~ Tip, data = tip_mod, alpha = 0.5, fill = ~ pref) +
  labs(title = "Density of Tips for Veg and Non-veg Preferences",
       x = "Tip Amount",
       y = "Food Preference") +
  scale_fill_manual(values = c("Veg" = "green", "Non-veg" = "red")) 


```

# Inference

-   Female students tend to tip slightly more, with an average tip of 12.17, compared to male students, who average around 10.17. This might hint at a marginally more generous tipping tendency among female students.

-   Vegetarian students show a higher average tip (12.33) than those who prefer non-veg options (10.00), suggesting a subtle association between vegetarian preference and a higher likelihood of tipping.

-   A large proportion of students in all groups did not tip, which might reflect a general attitude among college students that tipping is less essential or simply optional, potentially shaped by budget constraints common in student life.
