---
title: "Day2: Examining, Modifying and Grouping Datasets"
author: "Hardik Monga"
---

## Intro

Making a new post.

## Installing Libraries

```{r}
#| label: setup
library(tidyverse)
library(skimr)
library(knitr)
library(mosaic)
library(kableExtra)
```

## Look at the mpg dataset

```{r}
mpg %>%
  head(10)
```

## Ways to examine the mpg dataset

#### Glimpse

```{r}
glimpse(mpg)
```

#### Inspect

```{r}
mpg %>% mosaic::inspect()
```

#### Skim

```{r}
mpg %>% skimr::skim()
```

## Mutating mpg's variables to factors and saving them as mpg_modified

```{r}
mpg_modified <- mpg %>%
  dplyr::mutate(
    cyl = as_factor(cyl),
    fl = as_factor(fl),
    drv = as_factor(drv),
    class = as_factor(class),
    trans = as_factor(trans)
  )
glimpse(mpg_modified)
```

## Examining and Modifying babynames dataset

#### Import babynames dataset

```{r}
library(babynames)
```

#### babynames dataset

```{r}
babynames
```

#### Glimpse

```{r}
glimpse(babynames)
```

#### Inspect

```{r}
mosaic::inspect(babynames)
```

#### Skim

```{r}
skimr::skim(babynames)
```

#### Mutate babynames

```{r}
babynames_modified <- babynames %>%
  dplyr::mutate(
    year = as_factor(year),
    sex = as_factor(sex),
    name = as_factor(name),
    n = as_factor(n),
    prop = as_factor(prop)
  )
glimpse(babynames_modified)
```

#### Display babynames_modified

```{r}
babynames_modified
```

## Group by in mpg

```{r}
mpg_modified %>% filter(manufacturer == "audi") %>% 
  group_by(manufacturer, class, year) %>%
  summarize(average_cty = mean(cty), average_hwy=mean(hwy) )
```
