---
title: "Courses and Grades"
author: "Hardik Monga"
---

```{r}
library(tidyverse)
library(mosaic)
library(skimr)
library(dplyr)
library(ggformula)
library(crosstable)
```

```{r}
course<- read_delim(file = "../../data/course.csv")
course

inspect(course)
skim(course)
glimpse(course)
```

```{r}
hist(
    course$Score,
    breaks = 10,
    col = "lightblue",
    main = "Distribution of Scores",
    xlab = "Score",
    ylab = "Frequency"
)

```

```{r}
avg_score_year <- aggregate(Score ~ Year, data = course, FUN = mean)

# Line Plot
plot(
    avg_score_year$Year, avg_score_year$Score,
    type = "o",
    main = "Average Score Trend Across Years",
    xlab = "Year",
    ylab = "Average Score",
    pch = 16
)
```

```{r}
# Box Plot
boxplot(
    Score ~ Course,
    data = course,
    main = "Score Distribution Across Courses",
    xlab = "Course",
    ylab = "Score",
    las = 2
)

```

```{r}
# Scatter Plot
plot(
    course$Year, course$Score,
    col = ifelse(course$Gender == "F", "blue", "red"),
    pch = ifelse(course$Gender == "F", 16, 17),
    main = "Score vs Year with Gender Distinction",
    xlab = "Year",
    ylab = "Score"
)
legend("topright", legend = c("Female", "Male"), col = c("blue", "red"), pch = c(16, 17))

```

```{r}
gf_histogram(~Score,
  fill = ~Degree,
  data = course, alpha = .5
) %>%  gf_vline(xintercept = ~ mean(Score)) %>%
  gf_labs(
    title = "Degrees VS Scores",
    x = "Score", y = "Count"
  ) %>%
  gf_text(35 ~ (mean(Score)),
    label = "Mean",
  ) %>%
  gf_refine(guides(fill = guide_legend(title = "Degree")))

```

# Inference

-   The scores tend to remain within a similar range across different academic years, indicating consistent performance without significant changes in academic achievement as students progress.

<!-- -->

-   There isn’t a strong upward or downward trend in scores from year to year, suggesting that the academic difficulty or grading criteria may be consistent across years.

-   Both genders exhibit similar score distributions, with no notable performance differences between male and female students, suggesting equality in academic achievement.

-   A few outliers appear in the lower score ranges, showing that while most students score in a middle-to-high range, a minority are achieving significantly lower scores.

-   The majority of scores are concentrated in the mid-to-high range, indicating that most students perform relatively well, with fewer instances of extremely low or extremely high scores.
