---
title: "Money Spent"
author: "Hardik Monga"
---

```{r}
library(tidyverse)
library(mosaic)
library(skimr)
library(dplyr)
library(ggformula)
library(crosstable)
```

```{r}
money<- read_delim(file = "../../data/money.csv")
money

inspect(money)
skim(money)
glimpse(money)
```

```{r}
data_money <- as_tibble(money)

# Summarize data by gender
gender_spending <- data_money %>%
    group_by(Gender) %>%
    summarize(Total_Spent = sum(Money_spent, na.rm = TRUE))

# Bar plot
barplot(
    height = gender_spending$Total_Spent,
    names.arg = gender_spending$Gender,
    col = c("pink", "skyblue"),
    main = "Distribution of Spending by Gender",
    xlab = "Gender",
    ylab = "Total Money Spent"
)

```

```{r}
hist(
    data_money$Money_spent,
    breaks = 150,
    main = "Distribution of Money Spent",
    xlab = "Money Spent",
    ylab = "Frequency"
)
```

```{r}
# Box Plot
boxplot(
    Money_spent ~ Gender,
    data = money,
    main = "Money Spent by Gender",
    xlab = "Gender",
    ylab = "Money Spent",
    col = c("pink", "skyblue")
)

```

```{r}
pie(
    gender_spending$Total_Spent,
    labels = gender_spending$Gender,
    col = c("skyblue", "pink"),
    main = "Proportion of Total Money Spent by Gender"
)

```

```{r}

plot(
    density(data_money$Money_spent[data_money$Gender == "Male"], na.rm = TRUE),
    col = "blue",
    main = "Density of Money Spent by Gender",
    xlab = "Money Spent",
    ylab = "Density"
)
lines(density(data_money$Money_spent[data_money$Gender == "Female"], na.rm = TRUE), col = "pink")
legend("topright", legend = c("Male", "Female"), col = c("blue", "pink"), lty = 1)

```

# Inference:

-   **Gender-Based Spending Patterns**: There appears to be a difference in overall spending between genders, suggesting possible behavioral or situational factors influencing spending habits among male and female students.

<!-- -->

-   **High Spending Variability**: The range of money spent by students varies widely, indicating diverse financial behaviors or differing circumstances, with some students likely having significantly higher expenditures than others.

-   **Concentration Around Lower Spending Values**: Most students seem to spend within a lower range, implying a general trend toward modest spending, with only a few students deviating toward higher expenditures.
